Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-06-17 paper/tex/sections/methods.tex
actually finish methods proofread

\subsubsection{Detection rate calculation}
For any one instance of the Milky Way, we calculate the detection rate

For each physics variation model and DCO type, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation. This takes into account the true mass and IMF of the Milky Way since our simulations may each have a slightly different galaxy mass and only ever sample from massive stars rather than the full IMF. For a more in-depth discussion of this process see Appendix~\ref{app:rate_normalisation}.

>>>>

\subsubsection{Detection rate calculation}
For each physics variation model and DCO type, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation. This takes into account the true mass and IMF of the Milky Way since our simulations may each have a slightly different galaxy mass and only ever sample from massive stars rather than the full IMF. For a more in-depth discussion of this process see Appendix~\ref{app:rate_normalisation}.
